Open Data, Open Source and Open Standards in chemistry - The Blue Obelisk five years on

### 2011-05-13 paper.tex
Tidy up the text on InChI and add ref for JNI-InChI

The IUPAC InChI identifier is a non-proprietary and unique identifier
for chemical substances designed to enable linking of diverse data
compilations. Although its development predates the Blue Obelisk,
software such as Open Babel has included InChI support since 2005.
Since the official InChI implementation is in C, it is difficult to
access from the other widely used language for cheminformatics
toolkits, Java. The Blue Obelisk project JNI-InChI has been set up to
solve this problem by using the Java Native Interface to link the
InChI binary to Java. In this way, it promotes the wider adoption of
this standard identifier by the chemistry community.

Also, Indigo is going to provide its own plugin with an interface to
the InChI implementation in May 2011. This will enable developers to
calculate InChI and InChIKey-s within Python and .NET projects (not to
mention Java), eliminating the trouble of compiling and using binary
modules directly.

>>>>

The IUPAC InChI identifier is a non-proprietary and unique identifier
for chemical substances designed to enable linking of diverse data
compilations. Although its development predates the Blue Obelisk,
software such as Open Babel has included InChI support since 2005,
and support for InChI in Indigo is due in 2011.

Since the official InChI implementation is in C, it is difficult to
access from the other widely used language for cheminformatics
toolkits, Java. The Blue Obelisk project JNI-InChI~\cite{WebJNIInChI}
was established in 2006 to
solve this problem by using the Java Native Interface to link the
InChI binary to Java. In this way, it promotes the wider adoption of
this standard identifier by the chemistry community.
